---
title: "Alere & Tracking Merge"
output: html_notebook
---

Need: 


Do:
track (track.dedup) -> left merge w alere flu (alere.dedup) = have all tracked encounters in which there was alere done
left join with BO orders 

##Setup
```{r}
alere <- readRDS(file = "dfs/alere.dedup.Rda")
track <- readRDS(file = "dfs/track.dedup.Rda")
rvp <- readRDS(file = "dfs/rvp.Rda")
cxr <- readRDS(file = "dfs/cxr.dedup.Rda")

library(tidyverse)
library(lubridate)
library(psych)
```

##Merge Tracking with Alere
```{r}
track.alere <- merge(x = track,
                   y = alere,
                   by = "FIN",
                   all.x = TRUE)

track.alere %>% count(FluOverall)
```

##Merge Tracking+Alere with BO RVP Orders
```{r}
track.alere.bo <- merge(x = track.alere,
                   y = rvp,
                   by = "FIN",
                   all.x = T)
```

##Merge Tracking+Alere+BO with CXR
```{r}
track.alere.bo.cxr <- merge(x = track.alere.bo,
                       y = cxr,
                       by = "FIN",
                       all.x = TRUE)
```

##Cleanup Names
```{r}
#list column names
names(track.alere.bo.cxr)
track.alere.bo.cxr %>% count(MnemonicName)

```

```{r}
names(alere.flu.ili.neg)
```


```{r}
track.alere.bo.cxr.org <- track.alere.bo.cxr %>% select(FIN, Sex, DOB, Age,
                     RFV, RFV_ED, Dispo_ED,
                     Admit_DateTime, Arrival_DT, Reg_DT, Checkin_DT, TriageStart_DT, MDAssigned_DT, 
                     PinOrder_DT, TransferOrder_DT, BedAssign_DT, DischargeDecision_DT, Checkout_DT, Discharge_DateTime,
                     XR_OrderID, XR_Type, XR_OrderStatus, XR_OrderDT, XR_OrderCompleteDT,
                     OrderID, MnemonicName, OrderStatus, Order_DateTime, OrderComplete_DateTime, 
                     Alere_DateTime, FluA, FluB, FluOverall, Flags, Inconclusive)

saveRDS(track.alere.bo.cxr.org, file = "dfs/2ndx/track.alere.bo.cxr.org.Rda")
```


##Isolate Relevant Encounters

Load back in only needed df
```{r}
alltrack <- readRDS( file = "dfs/2ndx/track.alere.bo.cxr.org.Rda")
```

Columns
```{r}
names(alltrack)
```


Find orders which have no BO record but are in Alere (517 total)
```{r}
alltrack.i <- alltrack %>% filter(is.na(alltrack$MnemonicName) == TRUE & is.na(alltrack$FluOverall) == FALSE)
alltrack.i %>% count(FluOverall)
```

Find flu orders which have no Alere Record but are in BO (135 total)
```{r}
alltrack.i2 <- alltrack %>% filter(alltrack$MnemonicName == "Influenza (POCT)" & is.na(alltrack$FluOverall) == TRUE)
alltrack.i2 %>% count(MnemonicName)
```

Coerce "Influenza (POCT)" MnemonicName onto all Alere Exclusive Orders as MnemonicName2
```{r}
alltrack <- 
  alltrack %>% mutate(MnemonicName2 = case_when(
  (is.na(alltrack$MnemonicName) == TRUE & is.na(alltrack$FluOverall) == FALSE) ~ "Influenza (POCT)",
  TRUE ~ as.character(MnemonicName)
  ))

alltrack$MnemonicName2 <- factor(alltrack$MnemonicName2)

alltrack %>% count(MnemonicName2)
alltrack %>% count(MnemonicName)

```

Drop all orders without MnemonicName2
```{r}
only.rvp.selectvars <- alltrack %>% filter(is.na(MnemonicName2)==F)
only.rvp.selectvars %>% count(MnemonicName2)

saveRDS(only.rvp.selectvars, file="dfs/2ndx/only.rvp.selectvars.Rda")

only.rvp.selectvars %>% distinct(FIN)
```



Filter So Flu before and After
```{r}
df.flu.beforeafter2 <- 
  only.rvp.selectvars %>% filter(
  MnemonicName2 == "Respiratory PCR Panel" & Arrival_DT < as.Date("2018-10-01")|
  MnemonicName2 == "Influenza (POCT)" & Arrival_DT > as.Date("2018-10-01")
)

df.flu.beforeafter2 %>% count(MnemonicName2)

is.na(df.flu.beforeafter2$FluOverall) %>% summary()

n_distinct(df.flu.beforeafter2$FIN)

df.flu.beforeafter2 %>% count(OrderStatus)
```

Change Order Status to Complete for those with Alere match
```{r}
df.flu.beforeafter2 <- 
  df.flu.beforeafter2 %>% mutate(OrderStatus2 = case_when(
    is.na(FluOverall) == F ~ "Completed",
    TRUE ~ as.character(OrderStatus)
  ))
df.flu.beforeafter2$OrderStatus <- df.flu.beforeafter2$OrderStatus %>% 
  factor(levels = c("Completed", "Discontinued", "Canceled", "Voided", "Voided With Results"))

df.flu.beforeafter2$OrderStatus2 <- df.flu.beforeafter2$OrderStatus2 %>% 
  factor(levels = c("Completed", "Discontinued", "Canceled", "Voided", "Voided With Results"))

df.flu.beforeafter2 %>% count(OrderStatus2)
levels(df.flu.beforeafter2$OrderStatus2)
alltrack %>% count(MnemonicName)
```

Create NA Count
```{r}
df.flu.beforeafter2$NaCount <- df.flu.beforeafter2 %>% is.na() %>% rowSums()
```


Show Duplicates
```{r}
#create NA count
df.flu.beforeafter2.dup <- df.flu.beforeafter2[duplicated(df.flu.beforeafter2$FIN)|duplicated(df.flu.beforeafter2$FIN, fromLast = TRUE),] %>% #show encounters with duplicate FIN
 arrange(FIN, OrderStatus2, Inconclusive, Arrival_DT, Alere_DateTime, NaCount) #sort so inconclusive before postive before negative before invalid
```


Remove Duplicates
```{r}
#arrange
df.flu.beforeafter2 <- df.flu.beforeafter2 %>%
  arrange(FIN, OrderStatus2, Inconclusive, Arrival_DT, Alere_DateTime, NaCount)

#remove, resort, droplevels
df.flu.beforeafter2.dedup <- df.flu.beforeafter2 %>% distinct(FIN, .keep_all = TRUE) %>% arrange(Arrival_DT) %>% droplevels()

df.flu.beforeafter2 %>% count(MnemonicName2)
n_distinct(df.flu.beforeafter2.dedup$FIN)
```

Get Column Names
```{r}
names(df.flu.beforeafter2.dedup)
```

Rearrange Column Names
```{r}
df.flu.beforeafter2.dedup <- df.flu.beforeafter2.dedup %>% select(FIN, Sex, DOB, Age,
                     RFV, RFV_ED, Dispo_ED,
                     Admit_DateTime, Arrival_DT, Reg_DT, Checkin_DT, TriageStart_DT, MDAssigned_DT, 
                     PinOrder_DT, TransferOrder_DT, BedAssign_DT, DischargeDecision_DT, Checkout_DT, Discharge_DateTime,
                     XR_OrderID, XR_Type, XR_OrderStatus, XR_OrderDT, XR_OrderCompleteDT,
                     OrderID, MnemonicName, MnemonicName2, OrderStatus, OrderStatus2, Order_DateTime, OrderComplete_DateTime, 
                     Alere_DateTime, FluA, FluB, FluOverall, Flags, Inconclusive)
```


Export
```{r}
saveRDS(df.flu.beforeafter2.dedup, file = "dfs/2ndx/df.flu.beforeafter2.dedup.Rda")
```


```{r}
df.flu.beforeafter2$epi_week <- epiweek(df.flu.beforeafter2$Arrival_DT)
df.flu.beforeafter2$epi_year <- epiyear(df.flu.beforeafter2$Arrival_DT)
df.flu.beforeafter2$epi_yearweek <- if_else(df.flu.beforeafter2$epi_week<10, paste(df.flu.beforeafter2$epi_year, "-0", df.flu.beforeafter2$epi_week, sep = ""), paste(df.flu.beforeafter2$epi_year, df.flu.beforeafter2$epi_week, sep = "-"))
df.flu.beforeafter2 <- df.flu.beforeafter2 %>% arrange(Arrival_DT)

weekly.flu.lab <- df.flu.beforeafter2 %>% count(epi_yearweek)

library(ggpubr)
ggline(weekly.flu.lab, "epi_yearweek", "n")
```




