---
title: "Flu Before After Analysis "
output: html_notebook
---
##Setup
```{r}
#Import & libraries
flu <- readRDS(file = "dfs/df.flu.beforeafter.Rda")

library(tidyverse)
library(lubridate)
library(psych)
library(stargazer)
library(xtable)

```

##Compute Durations

```{r}
#Compute Bed Assigned to Discharge Decision
flu$BedToDispo.mins<- interval(ymd_hms(flu$BedAssign_DT), ymd_hms(flu$DischargeDecision_DT)) %>% as.duration()/dminutes(1)

#number of NAs in BedToDispo
is.na(flu$BedToDispo.mins) %>% table(flu$MnemonicName)
```

```{r}
#Compute AdmitToDischarge
flu$AdmitToDischarge.mins<- interval(ymd_hms(flu$Admit_DateTime), ymd_hms(flu$Discharge_DateTime)) %>% as.duration()/dminutes(1)

#number of NAs in AdmitToDischarge
is.na(flu$AdmitToDischarge.mins) %>% table(flu$MnemonicName)
```


##Traditonal Flu Outlier Removal
```{r}
#Remove extreme outliers by group (removes values >3IQR+3Q, LOS <15 min); 
flu1 <-flu %>% group_by(MnemonicName) %>% filter(!(AdmitToDischarge.mins > (quantile(AdmitToDischarge.mins, .75, na.rm=T)+3*IQR(AdmitToDischarge.mins, na.rm=TRUE))))
flu1 <- flu1 %>% group_by(MnemonicName) %>% filter(!(AdmitToDischarge.mins < 15))

#Remove predefined outliers (removes values LOS > 1 day, LOS <15 min); 
flu2 <- flu %>% group_by(MnemonicName) %>% filter(!(AdmitToDischarge.mins > 1440)) %>% filter(!(AdmitToDischarge.mins < 15))

#Remove predefined outliers (removes values LOS <15 min); 
flu2 <- flu %>% group_by(MnemonicName) %>% filter(!(AdmitToDischarge.mins < 20))
```

##Traditional Flu Homegeneity of Groups
###Sex Comparison
```{r}
flu2$Sex %>% ftable(flu2$MnemonicName)
chisq.test(flu2$MnemonicName, flu2$Sex, correct=FALSE)
```

###Age Comparison
```{r}
do.call("rbind", describeBy(flu2$Age, flu2$MnemonicName))
wilcox.test(Age ~ MnemonicName, data = flu2, alternative = "two.sided", var.equal = FALSE, conf.int = TRUE, conf.level = 0.95)
```

##Traditional Flu LOS Analysis
Shapiro Test - failed
```{r}
with(flu2, shapiro.test(AdmitToDischarge.mins[MnemonicName == "Influenza (POCT)"]))
with(flu2, shapiro.test(AdmitToDischarge.mins[MnemonicName == "Respiratory PCR Panel"]))
```

Wilcoxon test - significant
```{r}
do.call("rbind", describeBy(flu2$AdmitToDischarge.mins, flu2$MnemonicName)) %>% select(n, mean, median, min, max)
wilcox.test(AdmitToDischarge.mins ~ MnemonicName, data = flu2, alternative = "two.sided", var.equal = FALSE, conf.int = TRUE, conf.level = 0.95)
```

Bootstrapped Median CI
```{r}
library(rcompanion)
groupwiseMedian(data=flu2, AdmitToDischarge.mins ~ MnemonicName, bca = FALSE, percentile = TRUE, R = 1000)
```

##Traditional Flu Bed to Dispo Analysis

Shapiro Test - failed
```{r}
with(flu2, shapiro.test(BedToDispo.mins[MnemonicName == "Influenza (POCT)"]))
with(flu2, shapiro.test(BedToDispo.mins[MnemonicName == "Respiratory PCR Panel"]))
```

Wilcoxon test - significant
```{r}
do.call("rbind", describeBy(flu2$BedToDispo.mins, flu2$MnemonicName)) %>% select(n, mean, median, min, max)
wilcox.test(BedToDispo.mins ~ MnemonicName, data = flu2, alternative = "two.sided", var.equal = FALSE, conf.int = TRUE, conf.level = 0.95)
```

Bootstrapped Median CI
```{r}
library(rcompanion)
flu2.btd <- flu2 %>% filter(!is.na(BedToDispo.mins))
groupwiseMedian(data=flu2.btd, BedToDispo.mins ~ MnemonicName, bca = FALSE, percentile = TRUE, R = 1000)
```

##Traditional Flu CXR Analysis
Chi-square
```{r}
table(flu2$MnemonicName, flu2$XR_Completed)
chisq.test(flu2$MnemonicName, flu2$XR_Completed, correct = FALSE)
```

##Modified ILI Flu Setup
Subset by modified ILI
```{r}
#fever, cough, sore throat, flu, cold, body*ache, chills
flu.ili <- flu %>% subset(
  grepl("fever",flu$RFV, ignore.case=TRUE)| 
  grepl("cough",flu$RFV, ignore.case=TRUE)|
  grepl("sore.*throat",flu$RFV, ignore.case=TRUE)|
  grepl("throat.*pain",flu$RFV, ignore.case=TRUE)|
  grepl("flu",flu$RFV, ignore.case=TRUE)|
  grepl("cold",flu$RFV, ignore.case=TRUE)|
  grepl("body.*ache",flu$RFV, ignore.case=TRUE)|
  grepl("chills",flu$RFV, ignore.case=TRUE)
)

do.call("rbind", describeBy(flu.ili$AdmitToDischarge.mins, flu.ili$MnemonicName))
```

##Modified ILI Flu Homegeneity of Groups
###Sex Comparison
```{r}
flu.ili$MnemonicName %>% ftable(flu.ili$Sex)
chisq.test(flu.ili$MnemonicName, flu.ili$Sex, correct=FALSE)
```

###Age Comparison

```{r}
do.call("rbind", describeBy(flu.ili$Age, flu.ili$MnemonicName))
wilcox.test(Age ~ MnemonicName, data = flu.ili, alternative = "two.sided", var.equal = FALSE, conf.int = TRUE, conf.level = 0.95)
```


##Modified ILI Flu LOS Analysis
Shapiro Test - failed
```{r}
with(flu.ili, shapiro.test(AdmitToDischarge.mins[MnemonicName == "Influenza (POCT)"]))
with(flu.ili, shapiro.test(AdmitToDischarge.mins[MnemonicName == "Respiratory PCR Panel"]))
```

Wilcoxon test - significant
```{r}
do.call("rbind", describeBy(flu.ili$AdmitToDischarge.mins, flu.ili$MnemonicName)) %>% select(n, mean, median, min, max)
wilcox.test(AdmitToDischarge.mins ~ MnemonicName, data = flu.ili, alternative = "two.sided", var.equal = FALSE, conf.int = TRUE, conf.level = 0.95)
```

Bootstrapped Median CI
```{r}
library(rcompanion)
groupwiseMedian(data=flu.ili, AdmitToDischarge.mins ~ MnemonicName, bca = FALSE, percentile = TRUE, R = 1000)
```

##Modified ILI Flu Bed to Dispo Analysis

Shapiro Test - failed
```{r}
with(flu.ili, shapiro.test(BedToDispo.mins[MnemonicName == "Influenza (POCT)"]))
with(flu.ili, shapiro.test(BedToDispo.mins[MnemonicName == "Respiratory PCR Panel"]))
```

Wilcoxon test - significant
```{r}
do.call("rbind", describeBy(flu.ili$BedToDispo.mins, flu.ili$MnemonicName)) %>% select(n, mean, median, min, max)
wilcox.test(BedToDispo.mins ~ MnemonicName, data = flu.ili, alternative = "two.sided", var.equal = FALSE, conf.int = TRUE, conf.level = 0.95)
```

Bootstrapped Median CI
```{r}
library(rcompanion)
flu.ili.btd <- flu.ili %>% filter(!is.na(BedToDispo.mins))
groupwiseMedian(data=flu.ili.btd, BedToDispo.mins ~ MnemonicName, bca = FALSE, percentile = TRUE, R = 1000)
```

##Modified ILI Flu CXR Analysis

Chi-square
```{r}
table(flu.ili$MnemonicName, flu.ili$XR_Completed)
chisq.test(flu.ili$MnemonicName, flu.ili$XR_Completed, correct = FALSE)
```
